On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2025-11-28 char-4k-bound/char-4k-bound.tex
[4k3] Bibliography - Erdos
[4k3] Bibliography - VSU paper format
[4k3] Bibliography - translate the refs titles as required

N. H. Anning and P. Erdős, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{8} (1945), 598--600, \textsc{doi}: \href

@@

N. N. Avdeev, R. E. Zvolinsky, and E. A. Momot, On particular diameter bounds for integral point sets in higher dimensions
Proceedings of Voronezh State University. Series: Physics. Mathematics. 2025. No 1. Pp. 62-77.

@@

P. Erdős, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{12} (1945), 996, \textsc{doi}: \href

@@

A. Kemnitz, Punktmengen mit ganzzahligen Abständen, 1988.

@@

J. Solymosi and F. De Zeeuw, On a question of Erdős and Ulam, \emph{Discrete Comput. Geom.} 43.\textbf{2} (2010), 393--401,

@@

Н. Н. Авдеев, On integral point sets in special position, \emph{Некоторые вопросы анализа, алгебры, геометрии и
математического образования: материалы международной молодежной научной школы «Актуальные направления
математического анализа и смежные вопросы»} 8 (2018), 5--6.%

@@

Н. Н. Авдеев, Об отыскании целоудалённых множеств специального вида, Актуальные проблемы прикладной математики,
информатики и механики - сборник трудов Международной научной конференции. Научно-исследовательские публикации,

@@

М. Смуров and А. Спивак, Покрытия полосками, \emph{Квант} \textbf{5} (1998), 6--12.

>>>>

N. H. Anning and P. Erd{\H o}s, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{8} (1945), 598--600, \textsc{doi}: \href

@@

N. N. Avdeev, R. E. Zvolinsky, and E. A. Momot, On particular diameter bounds for integral point sets in higher dimensions,
\it{Proceedings of Voronezh State University. Series: Physics. Mathematics}. \textbf{1} (2025), 62--77.

@@

P. Erd{\H o}s, Integral distances, \emph{Bull. Amer. Math. Soc.} 51.\textbf{12} (1945), 996, \textsc{doi}: \href

@@

A. Kemnitz, Point sets with integer distances (Punktmengen mit ganzzahligen Abständen), 1988.

@@

J. Solymosi and F. De Zeeuw, On a question of Erd{\H o}s and Ulam, \emph{Discrete Comput. Geom.} 43.\textbf{2} (2010), 393--401,

@@

N. N. Avdeev, On integral point sets in special position,
\emph{Nekotorye voprosy analiza, algebry, geometrii i matematicheskogo obrazovaniya:
materialy mezhdunarodnoi molodezhnoi nauchnoi shkoly «Aktual'nye napravleniya matematicheskogo analiza i smezhnye voprosy»}
8 (2018), 5--6.%

@@

N. N. Avdeev,
On the search of special integral point sets
(Об отыскании целоудалённых множеств специального вида),
Aktual'nye problemy prikladnoj matematiki, informatiki i mekhaniki --- sbornik trudov Mezhdunarodnoj nauchnoj konferentsii,

@@

M. Smurov and A. Spivak, Covering by strips (Покрытия полосками), \emph{Kvant} \textbf{5} (1998), 6--12.
